--- 
title: "Python For Everything"
author: "Leon Xiao"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: xlhaw/xDocs
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Preface

Everything means nothing. Let's focus on the cv firstly.

Assume you already have some knowledge on.

```{python}

```
Not suitable for the narrative from beginning to the end.



```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

## Who this book is for

More practical way

## What this book covers
Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
Write something you don't master is agony. Where is your Muse? Spring/Source

From bit to 3d-print
0,1

Sensors -> 